Graphical formalization and automated computing of safety constraints in robotics

### 2012-08-12 paper/Paper.tex
"Not taken already" changed to "Not taken yet" in state machine

%\IEEEPARstart{S}{afety}
Safety critical applications require extensive testing or formal verification in order to achieve adequate safe and predictable behavior.
Even if a more highlevel program has no physical movements and thus cannot directly cause any damage, its output might still be a trigger for dangerous actions executed by interacting actors.
%Even if a more highlevel program has no physical actors and thus cannot cause any damage, it might still have dangerous effects on the environment.
Imagine a medication reminder application which guides a person through the process of medication intake. All interaction is done by showing textual instructions on a display. An error in the program logic could cause an already taken medication to be reminded again and may injure an Alzheimer's diseased person by medication overdosage.
This example is taken from a healthcare robotics project at the University of Auckland, New Zealand. Scientists are working on applications such as the medication reminder~\cite{medicationreminder} which run on mobile robots serving in nursing homes for the elderly. Equipped with a touch display and several external devices such as a blood pressure measurement tool the robots aim to support and entertain the elderly in their daily activities~\cite{5649910}\cite{healtbot_new}.
The applications are meant to be developed by healthcare professionals using Robostudio~\cite{robostudio}, a visual programming environment for rapid authoring and customization of complex services on a personal service robot.
%state machine based processes and a graphical tool for the designing of human robot interaction.
Generally these people don't have profound knowledge of the complex mathematical syntax used for formal verification methods such as computation tree logic (CTL) or linear temporal logic (LTL). Nevertheless certain safety guarantees must somehow be delivered in order to gain users' trust and to prevent any harm or injuries by the healthbots.
In case of the medication reminder mentioned above it mitght be important to ensure notifications are sent to staff members whenever medication is not taken by the patient, or to avoid duplicate reminders for medications which have already been taken.

@@

Unfortunately the supply of an easy-to-use editor for constraint creation doesn't guarantee adequate thinking about sufficent constraints by the developer. Unmotivated or just unexperienced developers may miss important constraints needed in order to achieve a certain safety level.
To support the user in finding significant constraints it might be useful to automatically compute constraint suggestions which make true testimonies about the current designed program. First of all the generated constraints provide an opportunity for the developer to identify reasonable constraints as well as contradictions between constraints and specification. The latter would mean there are errors in the program which lead to undesired constraints. Furthermore once constraints are created and checked for sanity they can be validated after every program change and thus ensure integrity during the development process.

In section~\ref{sec:automatedconstraintgeneration} we introduce an heuristic for finding reasonable safety constraints based on a state machine in the healthcare robotics domain.

>>>>

%\IEEEPARstart{S}{afety}
Safety critical applications require extensive testing or formal verification in order to achieve adequate safe and predictable behavior.
Even if a more highlevel program has no physical movements and thus cannot directly cause any damage, its output might still be a trigger for dangerous actions executed by interacting actors.
%Even if a more highlevel program has no physical actors and thus cannot cause any damage, it might still have dangerous effects on the environment.
Imagine a medication reminder application which guides a person through the process of medication intake. All interaction is done by showing textual instructions on a display. An error in the program logic could cause an already taken medication to be reminded again and may injure an Alzheimer's diseased person by medication overdosage.
This example is taken from a healthcare robotics project at the University of Auckland, New Zealand. Scientists are working on applications such as the medication reminder~\cite{medicationreminder} which run on mobile robots serving in nursing homes for the elderly. Equipped with a touch display and several external devices such as a blood pressure measurement tool the robots aim to support and entertain the elderly in their daily activities~\cite{5649910}\cite{healtbot_new}.
The applications are meant to be developed by healthcare professionals using Robostudio~\cite{robostudio}, a visual programming environment for rapid authoring and customization of complex services on a personal service robot.
%state machine based processes and a graphical tool for the designing of human robot interaction.
Generally these people don't have profound knowledge of the complex mathematical syntax used for formal verification methods such as computation tree logic (CTL) or linear temporal logic (LTL). Nevertheless certain safety guarantees must somehow be delivered in order to gain users' trust and to prevent any harm or injuries by the healthbots.
In case of the medication reminder mentioned above it might be important to ensure notifications are sent to staff members whenever medication is not taken by the patient, or to avoid duplicate reminders for medications which have already been taken.

@@

Unfortunately the supply of an easy-to-use editor for constraint creation doesn't guarantee adequate thinking about sufficent constraints by the developer. Unmotivated or just unexperienced developers may miss important constraints needed in order to achieve a certain safety level.
To support the user in finding significant constraints it might be useful to automatically compute constraint suggestions which make true testimonies about the current designed program. First of all the generated constraints provide an opportunity for the developer to identify reasonable constraints as well as contradictions between constraints and specification. The latter would mean there are errors in the program which lead to undesired constraints. Furthermore once constraints are created and checked for plausibility they can be validated after every program change and thus ensure integrity during the development process.

In section~\ref{sec:automatedconstraintgeneration} we introduce an heuristic method for finding reasonable safety constraints based on a state machine in the healthcare robotics domain.
